Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-27 paper/main.tex
add author contributions
reorganize supplementary sections in order

@@

%###################################################################################################
\subsection{Data Preparation (TODO)}
\begin{enumerate}
    \item Have masks of data; reference image segmantation tools; or do it by hand
    \item ensure that colors are matching for bacteria between time-steps
    \item clean borders of images if needed
    \item know domain size; otherwise use pixels
\end{enumerate}

@@

%###################################################################################################
\subsection{How to use obtained heterogenous results}
In order to reuse this model, we also provide the option to assign growth rates by sampling from a
normal distribution with user-defined parameters.

>>>>

\section{Author Contributions}
\textbf{Conceptualization:} Jonas Pleyer\\
\textbf{Investigation:} Jonas Pleyer\\
\textbf{Methodology} Jonas Pleyer\\
\textbf{Software:} Jonas Pleyer\\
\textbf{Supervision:} Christian Fleck\\
\textbf{Writing – original draft:} Jonas Pleyer\\
\textbf{Writing – review \& editing:} Jonas Pleyer \& Christian Fleck

@@

@@

%###################################################################################################
\subsection{Analysis \& Usage of heterogeneous Parameter Value (TODO)}
In order to reuse this model, we also provide the option to assign growth rates by sampling from a
normal distribution with user-defined parameters.

%###################################################################################################
\subsection{Application Data \& Preparation (TODO)}
\label{sec:supplement-data-details}

\begin{figure}[H]
    \centering
    % TODO include snapshots of utilized data
    \caption{TODO}
\end{figure}

\begin{enumerate}
    \item Have masks of data; reference image segmantation tools; or do it by hand
    \item ensure that colors are matching for bacteria between time-steps
    \item clean borders of images if needed
    \item know domain size; otherwise use pixels
\end{enumerate}
